---
title: "Midterm 1"
author: "YOUR NAME HERE"
output: html_document
editor_options: 
  chunk_output_type: console
---

### **Instructions**

Below is the Midterm 1 for DSCI 101 - Fall 2026. This exam should be written only by the student during exam hours. 

You are allowed to consult: 

* Class notes.
* Handwritten notes.
* Class R Scripts. 
* Class homework. 
* Help buttons in R. 

You are NOT allowed to: 

* Search for answers using search engines such as Google. 
* Search for answers using artificial intelligence programs such as ChatGPT.
* Consult with anyone 

**If you are found to be working with someone else or have used AI softwares to produce your answers, an automatic 0 will be given on the midterm exam and you will be reported to the Dean's Office.**

Write down your code inside the code chunk.

### **File submitted in HTML/PDF Format **

Submit the html/PDF file in Sakai before the deadline. Files in other format WILL NOT BE ACCEPTED.


### **Question 1**
 

#### 1.1
#(15 points)
Create a function to compute the total annual salary tax based on the state. 
For simplification, we only consider two states. In short, your function will contain two
arguments: (1) Salary; (2) State. The tax is the summation of federal and state tax.

Some basic information are given as follows:

Federal tax rate: 

| Income Range     | Rate |
| ---------------- | ---- |
| 0 – 11,000       | 10%  |
| 11001 – 44725    | 12%  |
| 44726 – 95375    | 22%  |
| 95376 – 182100   | 24%  |
| Above 182100     | 32%  |

Florida state tax rate: 0%

Illinois state tax rate:4.95%

Test your functions on the example `Tom (80000, IL)`

```{r}

```

#### 1.2
(10 points)
Utilize the for loop to test function defined in Question 1.1 on following information of four people. 

```{r}
name <- c("Tom","Peter","Emma", "Sophia")
salary <- c(50000, 70000, 200000, 110000)
state <- c("IL","FL","FL","IL")
```

For each iteration, print the sentence as, `name` comes from `state` and the tax is `your_answer_by_function`



```{r}

```
 
### **Question 2**

Use functions learned from the `tidyverse` package to complete this question. Load all the packages you will use throughout this exam in the loading packages section below.


### **Loading Packages**
(5 points)
```{r, message=FALSE, warning=FALSE}


```

#### 2.1
(5 points)
#Load the dataset `penguins` from the package.

#DO NOT PRINT THE DATA SINCE WE HAVE 344 rows

```{r}

```

#### 2.2 
(15 points)
Select the columns `island`, `bill length`and `body mass`. Define the new dataframe as `our_data`. DO NOT PRINT the resulting matrix, but you can check it by yourself.

```{r}

```


#### 2.3
(15 points)
With `our_data`, find the average `body mass` of the penguins on different islands.

Make sure there are no missing values in your final answer.

PRESENT the final answer.

```{r}

```

